CODECHECK: An open-science initiative to facilitate sharing of computer programs and results presented in scientific publications.

### 2020-12-14 codecheck-paper.tex
add Yale YARD

Local reproduction initiatives/services:
\href{https://ciser.cornell.edu/research/results-reproduction-r-squared-service/}{CISER R-squared}
(established/permanent),
\href{https://go.wwu.de/r2s2}{WWU R2S2} (pilot only, focused on reproductions),
\href{https://github.com/OxfordCodeReviewNet/forum}{Oxford code review network (OxCRN)}
(community, broader scope).
For these, the CODECHECK scope, tools, and practical experiences may be
helpful resources.

>>>>

Local reproduction initiatives/services:
\href{https://ciser.cornell.edu/research/results-reproduction-r-squared-service/}{CISER R-squared}
(established/permanent),
\href{https://go.wwu.de/r2s2}{WWU R2S2} (pilot only, focused on reproductions),
\href{https://github.com/OxfordCodeReviewNet/forum}{Oxford code review network (OxCRN)}
(community, broader scope), \href{https://isps.yale.edu/research/data/approach}{YARD 
at Yale} with dedicated staff for replications.
For these, the CODECHECK scope, tools, and practical experiences may be
helpful resources.
